Multi-task learning in Computer Vision

### 2020-04-01 1-Introduction.tex
Revert some changes

>>>>

\section{Scope of study}
In this thesis, we will study state-of-the-art solutions to some computer vision problems, like image classification, object detection, and text recognition. Then we will train classifiers that solve these problems using various data sets and try to combine them to produce a single multi-task network using multi-task learning. We will then evaluate how easy and effective it is to share the weights within similar and different tasks.

### 2020-04-01 3-Image-classification.tex
Revert some changes

\chapter{Transfer Learning}

@@

@@

>>>>

\chapter{Image classification}
Image classification is one of the essential modern computer vision problems, where the goal is to create a model that can classify an input image into one of a set of pre-defined classes. Before the popularization of applying large Convolutional Neural Networks for this task, the most successful way of solving the problem was to use some algorithm for finding feature descriptors in a set of images to construct a Visual Bag of Words.  A linear classifier, like a Support Vector Machine, would then do the classification using the Bag of Words representation of an image. These days nearly all approaches are based on using deep CNNs, and working CNNs were deployed already in 1998 on character recognition in the form of LeNet \citep{leNet}.

\section{ImageNet}

ImageNet  \citep{imagenet}  is perhaps the most significant dataset for image classification and especially the ImageNet Challenge \citep{ILSVRC}, which is a challenge for a collection of 1000 classes from the ImageNet dataset for image classification using 1.2 million training and 150 thousand test images of the entire ImageNet dataset. In 2012 the winning model, AlexNet \citep{alexNet}, showed that it was possible to train a deep CNNs efficiently using GPUs. Since 2012 all top-performing models showed some new improvements on how to create the most performant network architecture, for example, VGGNet from the year 2014 and ResNet \citep{resNet} from 2015, both of which have been popular models to use for Transfer Learning since.

Human accuracy on the ImageNet challenge is about 5.1\% \citep{imageNet_summary}, and ResNet achieves a top-5 error rate of 3.57\% \citep{resNet} and newer architectures even lower, but this still does not mean that image classification is a solved problem. The human performance experiment found that many of the human errors are caused by not having expert information in, for example, identifying animal species or not even being aware of the existence of a class \citep{imageNet_summary}. ObjectNet \citep{objectNet} is a dataset designed to test image classifiers with a focus on their generalizability. It contains many classes that also exist in the ImageNet dataset. However, they are in unexpected locations or have an unexpected pose, causing the high accuracy image classifiers trained on ImageNet to experience a 40-45\% accuracy drop when evaluating them on the ObjectNet images of classes shared between ImageNet and ObjectNet. This kind of adjustment is relatively easy for a human, and it shows that while the classifiers are good, they are by no means perfect.

@@

Unlike the ImageNet challenge, most real-world tasks do not have such an abundance of data for all possible classes. Still, to achieve the highest accuracies, they require models that are equal in terms of complexity to those that have top accuracies problems on the scale of the ImageNet classification. For this reason, many CNN classifiers, irrespective of the problem, feature one of the ImageNet classifiers in the model architecture. Even though some datasets may contain a large number of images per class, using a pre-trained classifier as a basis often produces a better final classifier by applying fine-tuning \citep{betterTransfer}.

@@

\section{ResNet}
ResNet is one of the first effective and very deep Convolutional Neural Network architecture that was presented in 2015 and won the ImageNet challenge. Prior to the publication of ResNet, the most powerful networks were relatively shallow, like VGGNet, which has only 19 layers. One of the big issues relating to training deep networks is vanishing gradients, where gradients disappear when they are backpropagated through many layers \citep{wideResNet}. ResNets utilize residual connections around bottleneck building blocks, which allow for the networks to contain many more layers than those without them, the largest network presented in the original ResNet paper was 152 layers, totaling for around 8x increase in the number of layers when compared to earlier networks \citep{resNet}.

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/resnet-block.png}
\caption{Resnet building block \citep{resNet}}
\end{figure}

The ResNet block architecture allows for the blocks to learn the identity function more efficiently by trying to learn the residual function instead of the direct mapping. Normally a mapping is learned between ${x}$ and ${y}$ using a function ${H(x)}$ but by the same token, we can learn a residual transformation, ${F(x) = H(x) - x}$, where ${H}$ is the mapping of two or more network layers. Both of these approaches should approximate the same functions; the difference is in how easy it is for the network to learn. Learning a transformation of ${F(x) = 0}$ would intuitively seem easier for a neural network than learning ${F(x) = x}$. As can be seen from the success of the ResNets compared to non-residual networks, this is what allows for creating very deep networks. If the transformation changes the input size, a matrix ${W}$ is necessary to map the input to the same dimensions, generating the final formula for a residual block ${y = F(x, \{W_i\}) + W_s x}$.

Many variants of ResNet exists, such as wide ResNets \citep{wideResNet}, ResNeXt \citep{resNext} and others. Also the DenseNet \citep{denseNet} is heavily inspired by ResNets. ResNet-50, ResNet-34, ResNet-101, and ResNet-152 are still some of the most popular models to use when a pre-trained ImageNet trained backbone is needed for some part of a classifier as they produce good results and do not contain too many parameters compared to some other architectures.

\section{Improving model performance}
Improving model performance is not easy, but using the various types of skip-connections, such as the ones used in ResNet residual blocks, it is possible to increase the size of the network to massive sizes. A 557 million parameter model called GPipe \citep{gPipe} takes the model scaling to the extreme and requires some unique parallelism libraries to train the model. It is still only slightly better than previous models, showing that size is not the only thing that matters.

\begin{figure}[h!] 
\centering 
\includegraphics[width=0.8\textwidth]{imgs/scaling-networks.png}
\caption{Various ways of scaling network architectures \citep{efficientNet}}
\end{figure}

There are three main ways to scale up a network, as shown in figure 3.3. Scaling by depth means adding more layers to the model, allowing for more complex dependencies to be captured by the model. For example, ResNet-1000 is a very deep type of ResNet, but it has similar performance to a ResNet-101, so there are diminishing returns when trying to scale up by depth \citep{efficientNet}. Scaling by width means increasing the number of channels in the layers, and it is especially popular when optimizing smaller size models, such as MobileNet \citep{mobileNet}. Wide ResNets \citep{wideResNet} increase the width of the ResNet blocks and allow for better features and easier training. The third way is to increase the resolution of the input. A higher resolution allows for the network to find more specific features as the level of detail increases, and often specific network architectures work best at one particular resolution.

The other approach to finding a better architecture is to use different kinds of blocks that are better. One way of finding better building blocks is by manual experimentation. The other, like in the case of MnasNet \citep{mnas}, is to pose the problem as an optimization problem and to use Neural Architecture Search \citep{neuralSearch} to find the optimal solution. In the case of MnasNet, the goal is to maximize m in ${ACC(m) \times [\frac{LAT(m)}{T}]^w}$, where ${T}$ is the target, by searching in a constrained space. So the goal is to optimize the accuracy with a given latency on a specific device. The search produces small but very efficient models when the target device is a mobile phone.

\section{EfficientNet}
EfficientNet models form a family of models ranging from EfficientNet0 to EfficientNet7 that were generated by smartly scaling existing convolutional models to optimize them for efficiency in a similar way to MnasNet \citep{efficientNet}. The more complex models are created by using compound scaling on the EfficientNet0 model, shown in Figure 3.3 (e),  where the width, depth, and the resolution of the network are scaled using a factor ${\phi}$. As the cost of neural architecture search grows exponentially as the size of the network grows, the search is only done on the base model. The search of ${\phi}$ is a constrained optimization problem, where width, depth and, resolution are constrained such that ${d^\phi \times w^\phi \times r^\phi \approx 2}$ and each increase in ${\phi}$ increases network FLOPS by ${2^\phi}$. The architecture search for the base network is similar to that of MnasNet. The target of EfficinetNet is  ${ACC(m) \times [\frac{FLOPS(m)}{T}]^w}$, so the goal is to optimize for both accuracy and number of floating-point operations instead of latency as in MnasNet \citep{efficientNet}.

As seen in figure 3.1, these optimizations allow for the EfficientNet to form a very performant architecture using a low amount of parameters that does well on ImageNet and is good at Transfer Learning also. Interestingly though, the reduction in FLOPS and parameters do not directly translate to low real-world inference time. As is compared in the paper, an EfficientNet-B1 gets a 5.7x speedup over a ResNet-152, while the EfficientNet scores significantly higher on ImageNet. So in terms of the time and accuracy ratio, the EfficientNet seems to do well. When looking at the inference time in terms of FLOPS and parameters, we can find out that the ResNet would be more efficient, as the ResNet has 7.6x as many parameters and 16x FLOPS when compared to the EfficientNet, but the inference time multiplier is 5.7x. From this comparison, we can easily see that the number of FLOPS is not a direct proxy for inference time and instead the optimization should be for latency directly as in MnasNet if that is the goal.

The proposed EfficientNet models use mobile inverted bottleneck (MBConv) blocks used in MobileNetV2 \citep{mobileNetv2} in constructing the base model. The MobileNet uses a Depthwise Separable Convolution, where a depthwise convolution and a pointwise convolution are applied in sequence. The depthwise convolution applies ${d_i}$ ${k x k}$ filters to the input, where ${d_i}$ is the input channels and ${k}$ is the kernel size leading to an output channel count ${d_j = d_i}$. A normal convolutional layer would apply multiple filters having ${M}$ channels with the computational cost of ${h_i w_i d_i d_j k^2}$, whereas the depthwise convolution only has a cost of ${h_i w_i d_i (k^2 + d_j)}$, reducing the cost by ${k^2}$. The result of the depthwise convolution then runs through a pointwise convolution, where a ${1 \times 1 \times d_j}$ 1d convolution is applied to get the final output as a linear combination of the channels. The inverted residuals in MBConv are connections similar to ResNet, but in this case they are connected between the low dimensional layers.
